Twists of supersymmetric gauge theories

### 2019-11-04 paper.tex
typo fix
Vector multiplet SUSY

\newcommand{\Dens}{\mathrm{Dens}}

@@

\subsubsection{Super Yang--Mills Theory} \label{YM_section}

@@

Fix a Lie algebra $\fg$ equipped with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle$ and a spinorial representation $\Sigma$ of $\so(V)$ with an $\so(V)$-equivariant pairing $\Gamma \colon \Sym^2(\Sigma)\to V$ (see Section \ref{sec: susy} for more details on supersymmetry). The fields of super Yang--Mills theory are the following:
\begin{itemize}
\item A connection $A \in \Omega^1(V_\RR; \fg)$ on the trivial bundle.

@@

Denote by $F_A = \d_{\dR} A + \frac{1}{2}[A\wedge A]$ the curvature of $A$ and let $\sd D_A \colon \Sigma \to \Sigma^*$ be the Dirac operator obtained from $\Gamma$ (see Section \ref{sec: susy}). We denote by $\sd\d$ the Dirac operator for the zero connection.

The BRST action is given by
\[S(A, \lambda) = \int_{V_\RR} \left\langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\right\rangle.\]

The associated BV theory $(E, Q, \omega, I)$ is given as follows (see also \cite[Section 3.1]{ElliottYoo1}). Let $A^*, \lambda^*, c^*$ be the antifields corresponding to $A, \lambda, c$ respectively. The bundle of BV fields is
\[E = \Omega^1(V_\RR; \fg)\oplus \Omega^0(V_\RR; \Pi\Sigma\otimes \fg)\oplus \Omega^0(V_\RR; \fg)[1] \oplus \Omega^{n-1}(V_\RR; \fg^*)[-1]\oplus \Omega^n(V_\RR; \Pi\Sigma^*\otimes \fg^*)[-1]\oplus \Omega^n(V_\RR; \fg^*)[-2].\]
The pairing $\omega$ on $E$ is induced by the evaluation pairings $\gg^*\otimes \gg\rightarrow \CC$ and $\Sigma^*\otimes\Sigma\rightarrow\CC$. The BV action is given by
\[S_{BV} = \int_{V_\RR} \left\langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\right\rangle + (A^*, \d_A c) + (\lambda^*, [\lambda, c]).\]

@@

The Poincar\'e group acts, in the sense of Definition \ref{group_action_def}, on Yang--Mills theory on $\RR^n$ for any choice $\Sigma$ of matter representation. Indeed, there is an obvious Poincar\'e action on fields where we use that $\Sigma$ is a representation of $\Spin(V_\RR)$. The corresponding Hamiltonian is given by
\[
I_{\mr{Poin}}(v) = \int_{V_\RR} (v.A) \wedge A^* + (v.\lambda) \lambda^* + (v.c)c^*,
\]
where $v\in\mf{iso}(V)$.

@@

\subsection{Supersymmetric Yang-Mills Theory} \label{SUSY_action_section}
For minimal choices of the spinorial representation, Yang-Mills theory admits an action of the supersymmetry algebra when $n=3,4,6$ or 10.  In this subsection we will construct these supersymmetry algebra actions.

In this section, we will consider pairs $(\mf A, \fL)$ consisting of a supersymmetry algebra and an instance of Yang-Mills theory with matter, in one of the following four situations.
\begin{itemize}
 \item Dimension $n=3$ with $\Sigma = S$, the 2-dimensional Dirac representation.
 \item Dimension $n=4$ with $\Sigma = S_+ \oplus S_-$, 4-dimensional Dirac representation.
 \item Dimension $n=6$ with $\Sigma = S_+ \otimes W$ where $W$ is a 2-dimensional symplectic vector space, the 8-dimensional symplectic Weyl representation.
 \item Dimension $n=10$ with $\Sigma = S_+$, the 16-dimensional Weyl representation.
\end{itemize}

\begin{definition}
In each case we will write $\wt \Sigma$ for the spin representation obtained from $\Sigma$ by parity reversal, so in dimensions 3 and 4 $\wt \Sigma = \Sigma$, in dimension 6 $\wt \Sigma = S_- \otimes W$, and in dimension 10 $\wt \Sigma = S_-$.
\end{definition}

We'll construct, in each of these cases, an $L_\infty$ action of the super Lie algebra $\mf A$ on the theory $\fL$.  This construction will proceed in two steps.
\begin{enumerate}
 \item There is an ordinary Lie action of the super Lie algebra $\mf A$ on the theory $\fL$, extending the standard action of the $n$-dimensional Poincar\'e algebra by isometries of $\RR^{n}$ as discussed in Section \ref{YM_section}, which is only well-defined on-shell.  In other words, there is a linear map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ which is a Lie action modulo the ideal generated by the equations of motion.
 \item We can promote this on-shell action to an $L_\infty$ map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ by including a quadratic term $\delta^{(2)}$ which ``corrects'' for the failure of the map $\delta^{(1)}$ to be a Lie map on-the-nose.
\end{enumerate}
This construction only works in the four special dimensions $3,4,6$ and 10: our argument will use results of Baez and Huerta \cite{BaezHuerta} proven using the structure of the four normed division algebras $\RR, \CC, \bb H$ and $\bb O$.  In particular, we will use the following ``3-$\psi$'s rule'', discussed in the 10-dimensional case by Schray \cite{Schray} .  Let $g(v,w)$ denote the Riemannian metric on $\RR^n$.

\begin{theorem}[{\cite[Theorem 11]{BaezHuerta}}] \label{3_psi_thm}
The multilinear map 
\[T \colon \Sigma \otimes \Sigma \otimes \Sigma \otimes \Sigma \to \CC,\]
obtained by symmetrizing the expression $g(\Gamma(\psi_1,\psi_2), \Gamma(\psi_3, \psi_4))$ in the first three variables, is zero.
\end{theorem}

We'll begin with a discussion of the on-shell supersymmetry action, discuss its failure to close off-shell, and then derive the $L_\infty$-correction to this failure.  Then we'll state and prove the main theorem of this section: the fact that our super Yang-Mills theories are supersymmetric.

So, we start by discussing the on-shell supersymmetry.  The fermionic part of the supersymmetry algebra is defined by saying that $Q \in \Sigma$ acts infinitesimally by
\[
\begin{pmatrix}
A \\ \lambda
\end{pmatrix}
\mapsto
\begin{pmatrix} A + \delta_Q A \\
\lambda + \delta_Q \lambda
\end{pmatrix}
\]
where 
\begin{align*}
\delta_Q A &= \Gamma(Q,\lambda) \\
\delta_Q \lambda &= \sd F_A Q .
\end{align*}
Here, the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F_{ij} \gamma^i \gamma^j$.  We can check that this supersymmetry action does not close off-shell.

\begin{lemma} \label{onshell_action_lemma}
Suppose $Q_1, Q_2 \in \Sigma$ and $(A, \lambda)$ are super Yang-Mills fields.
The following relations hold:
\begin{itemize}
\item[(1)] \label{10dsusyA} $ [\delta_{Q_1}, \delta_{Q_2}] A = \delta_{[Q_1, Q_2]} A$.
\item[(2)] \label{10dsusyL} $ [\delta_{Q_1}, \delta_{Q_2}] \lambda = \delta_{[Q_1,Q_2]} \lambda - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_2, \sd \dd \lambda)Q_1 - \frac 12(Q_2, \sd \dd \lambda)Q_2$ .
\end{itemize}
Here, the commutator on the left hand side of the equations takes place in the algebra of endomorphisms of the space of fields.
\end{lemma}

We'll prove this lemma after first translating it into more convenient language: the terminology of the equivariant action functional, as introduced in Section \ref{symmetry_section}.  Our Lemma \ref{onshell_action_lemma} tells us that the supersymmetry action is a Lie algebra homomorphism only modulo the ideal generated by the equation of motion $\sd \dd \lambda = 0$.
In other words, this supersymmetry action only defined an action of the Lie algebra of supertranslations ``on-shell".  This calculation suggests introducing a second order correction to the supersymmetry action on the BV theory, which has the chance of closing off-shell.  Define a second order action depending on the antifield $\lambda^*$ to the gluino $\lambda$ by
\begin{align*}
\delta^{(2)} \colon \Sigma \otimes \Sigma \otimes \Gamma(\RR^{n}; \Pi \wt \Sigma[-1]) &\to \Gamma(\RR^{n}; \Pi \Sigma) \\
Q_1 \otimes Q_2 \otimes \lambda^* &\mapsto - \left(\rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right).
\end{align*}

We'll rewrite this as a local functional in the theory $\fL$ coupled to the supersymmetry Lie algebra $\mf A$.

\begin{definition}
The off-shell supersymmetry action on complexified Yang-Mills theory on $\RR^{n}$, for $n=3,4,6,10$, is defined to be the cochain
\[I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL),\]
where 
\begin{align*}
I^{(1)} (Q ; A, \lambda, A^*, \lambda^*) & = \<A^* , \Gamma(Q, \lambda)\> + \<\lambda^*, \sd F_A Q\> \\
I^{(2)} (Q_1,Q_2 ; \lambda^*) & =  \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
\end{align*}
\end{definition}

We can rephrase Lemma \ref{onshell_action_lemma} in terms of these local functionals, using the interpretation where 
\begin{align*}
I^{(1)}(Q) &= \<A^* , \delta_{Q} A\> + \<\lambda^*, \delta_{Q_1} \lambda\> \\
\text{and } I^{(2)}(Q_1,Q_2) &= \<\lambda^*, \delta^{(2)}_{Q_1,Q_2}\lambda\>.
\end{align*}
Let us write $\d_{\mr{CE}}^\Gamma$ for the Chevalley-Eilenberg differential associated to the \emph{supertranslation algebra} $\CC^m \oplus \Pi \Sigma$, with bracket given by the pairing $\Gamma$.  We include the superscript $\Gamma$ here to distinguish this differential from the Chevalley-Eilenberg differential in the full super Poincar\'e algebra, which we will use below.

\begin{lemma} \label{onshell_interaction_lemma}
The functionals $I^{(1)}$ and $I^{(2)}$ above satisfy the equation
\[\{I^{(1)},I^{(1)}\} + \d_{\mr{CE}}^\Gamma I^{(1)} = -2\{S_{\mr{BV}} , I^{(2)}\}.\]
\end{lemma}

\chris{Pavel wants to replace these two proofs: first of Lemma \ref{onshell_action_lemma}, then of Lemma \ref{onshell_interaction_lemma}, with a single coordinate free argument.}
\begin{proof}[Proof of Lemma \ref{onshell_action_lemma}]
Both of the two statements are direct calculations using standard Clifford relations which cite below.
So, we calculate
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] A &= (\Gamma(Q_2,\sd F_A Q_1) + \Gamma(Q_1,\sd F_A Q_2)) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_1 \gamma^k \gamma^j \gamma^i Q_2) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
&= F_{ij}(\delta^{jk}(Q_2\gamma^i Q_i) - Q_2 \gamma^i \gamma^j \gamma^k + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
&=  F_{ij}\delta^{jk}(Q_2 \gamma^i Q_1) \\
&= \delta_{[Q_1, Q_2]} A,
\end{align*}
where on the third line we used the fact that the pairing $\Gamma(-,-)$ is symmetric -- i.e. that $\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$ -- and on the fourth line we used the Clifford relation $\gamma^j\gamma^j+\gamma^j\gamma^j = \delta^{jk}$.

\brian{Here's the coordinate free argument. 
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] A &= (\Gamma(Q_2,\sd F_A Q_1) + \Gamma(Q_1,\sd F_A Q_2)) \\ 
& = i_{[Q_1,Q_2]} (F_A) \\ & = L_{[Q_1,Q_2]} (A) + \d_A(i_X A) .
\end{align*}
In the second line we have used the identity 
\[
\Gamma(Q_1, \rho(\omega) Q_2) + \Gamma(Q_2, \rho(\omega) Q_1) = i_{[Q_1,Q_2]} (\omega)
\]
which holds for every two-form $\omega$. 
}
Note that, on the gauge fields, the action is a Lie action on the nose, not only on-shell.  Similarly we can calculate, (as in \cite{Guillen}):
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= (\sd F_{\Gamma(Q_2, \lambda)} Q_1 + \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
&= \frac 12((Q_2 (\gamma_j \dd_i - \gamma_i \dd_j) \lambda) (\gamma^i \gamma^j Q_1) + (1 \leftrightarrow 2)) \\
&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) - \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_2) \\
&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) + \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^j \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^j \gamma^i Q_2) + \\
&\quad - \frac 12((Q_2 \gamma_i \dd_j \lambda) \delta_{ij} Q_1 + \frac 12(Q_1 \gamma_i \dd_j \lambda) \delta^{ij} Q_2) \\
&= ((Q_1 \gamma_j Q_2) (\gamma^i \gamma^j \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2
\end{align*}
using the fact that 
\[(\psi_1 \gamma_j \psi_2)(\gamma^j \psi_3) + (\psi_2 \gamma_j \psi_3)(\gamma^j \psi_1) + (\psi_3 \gamma_j \psi_1)(\gamma^j \psi_2) = 0,\]
as in Theorem \ref{3_psi_thm}.  Making one more simplification using the Clifford relations, we have
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= ((Q_1 \gamma_j Q_2) (\delta^{ij} \dd_i \lambda) - ((Q_1 \gamma_j Q_2) (\gamma^j \gamma^i \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2 \\
&= \delta_{[Q_1,Q_2]} \lambda - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_2, \sd \dd \lambda)Q_1 - \frac 12(Q_2, \sd \dd \lambda)Q_2.
\end{align*}
\end{proof}

>>>>

\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\Dens}{\mathrm{Dens}}

@@

\subsubsection{Yang--Mills Theory with Spinorial Matter} \label{YM_section}

@@

Fix a Lie algebra $\fg$ equipped with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle$ and a spinorial representation $\Sigma$ of $\so(V)$ with an $\so(V)$-equivariant pairing $\Gamma \colon \Sym^2(\Sigma)\to V$. We define the Clifford action $\rho\colon V\rightarrow \hom(\Sigma, \Sigma^*)$ by
\begin{equation}
(\rho(v) Q_1, Q_2) = (v, \Gamma(Q_1, Q_2))
\label{eq:Gammaspinorpairing}
\end{equation}
for any $Q_1, Q_2\in\Sigma$ and $v\in V$.

The fields of Yang--Mills theory are as follows:
\begin{itemize}
\item A connection $A \in \Omega^1(V_\RR; \fg)$ on the trivial bundle.

@@

Denote by $F_A = \d_{\dR} A + \frac{1}{2}[A\wedge A]$ the curvature of $A$ and let $\sd D_A \colon \Sigma \to \Sigma^*$ be the Dirac operator obtained from $\Gamma$ (see Section \ref{sec: susy}).

The BRST action is given by
\[S(A, \lambda) = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd D_A \lambda)\right\rangle.\]

The associated BV theory $(E, Q, \omega, I)$ is given as follows (see also \cite[Section 3.1]{ElliottYoo1}). Let $A^*, \lambda^*, c^*$ be the antifields corresponding to $A, \lambda, c$ respectively. The bundle of BV fields is
\[E = \Omega^1(V_\RR; \fg)\oplus \Omega^0(V_\RR; \Pi\Sigma\otimes \fg)\oplus \Omega^0(V_\RR; \fg)[1] \oplus \Omega^{n-1}(V_\RR; \fg^*)[-1]\oplus \Omega^n(V_\RR; \Pi\Sigma^*\otimes \fg^*)[-1]\oplus \Omega^n(V_\RR; \fg^*)[-2].\]
The pairing $\omega$ on $E$ is induced by the evaluation pairings $\gg^*\otimes \gg\rightarrow \CC$ and $\Sigma^*\otimes\Sigma\rightarrow\CC$. The BV action is given by
\[S_{BV} = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd D_A \lambda)\right\rangle - (\d_A c, A^*) + ([\lambda, c], \lambda^*) + \frac{1}{2}([c, c], c^*).\]

@@

The Poincar\'e group acts, in the sense of Definition \ref{group_action_def}, on Yang--Mills theory on $\RR^n$. Indeed, there is an obvious Poincar\'e action on fields where we use that $\Sigma$ is a representation of $\Spin(V_\RR)$. The corresponding Hamiltonian is given by
\begin{equation}
I^{(1)}(v) = \int_{V_\RR} -(L_{v}A, A^*) - (v.\lambda, \lambda^*) - (v.c)c^*,
\label{eq:Poincareaction}
\end{equation}
for $v\in\mf{iso}(V)$, where $v.\lambda$ contains both a derivative and the $\so(V)$ action on $\Sigma$.

@@

\subsection{Vector multiplet} \label{sect:vectormultipletSUSY}

For certain choices of the spinorial representation, the Yang--Mills theory from Section \ref{YM_section} admits an action of supersymmetry. In this section we consider pairs consisting of a supersymmetry algebra and an instance of Yang--Mills theory with matter, in one of the following four situations:
\begin{itemize}
 \item Dimension $n=3$ with $\Sigma = S$, the 2-dimensional Dirac representation.
 \item Dimension $n=4$ with $\Sigma = S_+ \oplus S_-$, 4-dimensional Dirac representation.
 \item Dimension $n=6$ with $\Sigma = S_+ \otimes W$ where $W$ is a 2-dimensional symplectic vector space, the 8-dimensional symplectic Weyl representation.
 \item Dimension $n=10$ with $\Sigma = S_+$, the 16-dimensional Weyl representation.
\end{itemize}
These correspond to the 3d $\cN=1$, 4d $\cN=1$, 6d $\cN=(1, 0)$ and 10d $\cN=(1, 0)$ vector multiplets respectively.

We will construct, in each of these cases, an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory. Following Definition \ref{infinitesimal_action_def}, we have to construct a collection of functionals $I^{(1)}, I^{(2)}, \dots$, where $I^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, satisfying the classical master equation. The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:Poincareaction}, so we just have to specify the values of $I^{(k)}$ on the supersymmetry generators in $\Sigma$.

Recall that $\Gamma\colon\Sym^2(\Sigma)\rightarrow V$ gives rise to an action map
\[\rho\colon V\otimes \Sigma\longrightarrow \Sigma^*\]
by \eqref{eq:Gammaspinorpairing}. We may also identify $\wedge^2(V)\rightarrow \so(V)$ via
\[\omega\mapsto (w\mapsto -2\iota_{(w, -)} \omega).\]
This gives rise to an action map
\[\wedge^2(V)\otimes \Sigma\longrightarrow \Sigma\]
of two-forms on spinors. Finally, we choose a pairing $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ which again induces an action map $\rho\colon V\otimes \Sigma^*\rightarrow \Sigma$ which satisfies the Clifford relation
\[\rho(v_1)\rho(v_2) + \rho(v_2)\rho(v_1) = 2(v_1, v_2)\]
on $\Sigma$ and $\Sigma^*$.

\begin{thm}
The functional $I_\rho = I_{BV} + I^{(1)} + I^{(2)}$ with
\begin{align*}
I^{(1)}(Q) &= \int (\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A), \lambda^*) \\
I^{(2)}(Q_1, Q_2) &= \int \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*
\end{align*}
satisfies the classical master equation
\[(Q+\d_{CE}) I_{\rho} + \frac{1}{2}\{I_\rho, I_\rho\} = 0.\]
\label{thm:vectormultipletSUSY}
\end{thm}

The rest of the section will be devoted to the proof of the above theorem.

Consider the map $q\colon \wedge^\bullet(V)\rightarrow \Cl(V)$ given by antisymmetrization, so that, for instance,
\begin{equation}
q(v_1\wedge v_2) = v_1v_2 - (v_1, v_2).
\label{eq:quantizationtwoforms}
\end{equation}

The resulting action $\wedge^2(V)\otimes \Sigma\rightarrow \Sigma$ then coincides with the original action of $\so(V)$ on the spinorial representation $\Sigma$.

The following properties of the Clifford action will be useful. Here the first property expresses $\so(V)$-invariance of the pairing $\Gamma\colon\Sigma\otimes \Sigma\rightarrow V$, the second property follows from \eqref{eq:quantizationtwoforms} and the third property was proved in \cite[equation 7.6]{Snygg}.

\begin{prop}
One has the following:
\begin{enumerate}
\item For $X\in\wedge^2(V)$ and $Q_1,Q_2\in\Sigma$ we have
\[\Gamma(Q_1, \rho(X) Q_2) + \Gamma(Q_2, \rho(X) Q_1) = -2\iota_{\Gamma(Q_1, Q_2)} X.\]

\item Suppose $Q_1,Q_2\in\Sigma$ and $\lambda\in\Gamma(M, \Sigma\otimes \fg)$. Then
\[\sd{D}_A\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d_A \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{D}_A \lambda) Q_2.\]

\item Suppose $Q\in\Sigma$ and $X\in\Omega^2(M; \fg)$. Then
\[\sd{D}_A(\rho(X) Q) = \rho(d_A X)Q + (-1)^n\rho(\ast d_A\ast X) Q.\]
\end{enumerate}
\label{prop:cliffordactionproperties}
\end{prop}

In addition, we have the following important property of the $\Gamma$-pairing which holds in the above cases. This was proved in \cite{Schray} in dimension 10 and explained in \cite{BaezHuerta} using division algebras in all dimensions.

\begin{prop}
Suppose $Q_1, Q_2, Q_3\in\Sigma$. Then
\[\rho(\Gamma(Q_1, Q_2))Q_3 + \rho(\Gamma(Q_2, Q_3))Q_1 + \rho(\Gamma(Q_3, Q_1))Q_2 = 0.\]
\label{prop:3psi}
\end{prop}

We are now ready to prove Theorem \ref{thm:vectormultipletSUSY}. The classical master equation decomposes into the following equations:
\begin{align*}
\{S_{BV}, I^{(1)}\} &= 0 \\
\{S_{BV}, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2}\{I^{(1)}, I^{(1)}\} &= 0 \\
\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} &= 0 \\
\{I^{(2)}, I^{(2)}\} &= 0.
\end{align*}

Note that the last equation is automatically satisfied since $I^{(2)}$ is independent of $\lambda$ and $c$. The rest of the claims will be proved in a sequence of Lemmas. To simplify the expressions, we drop the integrals and omit the natural pairings.

\begin{lemma}
One has $\{S_{BV}, I^{(1)}(Q)\} = 0$.
\end{lemma}
\begin{proof}
Let us decompose $S_{BV} = \sum_{i=1}^5 S_{BV}^i$ into individual summands.

The first term gives
\begin{align*}
\{S_{BV}^1, I^{(1)}(Q)\} &= -\frac{1}{2} d_A \Gamma(Q, \lambda)\wedge \ast F_A\\
&= -\frac{1}{2} \Gamma(Q, \lambda)\wedge d_A \ast F_A \\
&= -\frac{1}{2}(-1)^{n-1} d_A\ast F_A\wedge \Gamma(Q, \lambda) \\
&= -\frac{1}{2}(-1)^{n-1} (\ast d_A \ast F_A, \Gamma(Q, \lambda)).
\end{align*}

The second term gives
\begin{align*}
\{S_{BV}^2, I^{(1)}(Q)\} &= -\frac{1}{2}(\lambda, \rho(\Gamma(Q, \lambda))\lambda) + \frac{1}{2}(\rho(F_A) Q, \sd{D}_A\lambda) \\
&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda))  - \frac{1}{2}(\lambda, \sd{D}_A(\rho(F_A) Q)) \\
&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) - \frac{1}{2} (-1)^n (\lambda, \rho(\ast d_A\ast F_A) Q),
\end{align*}
where we have used Proposition \ref{prop:cliffordactionproperties} (property (3)) and the Bianchi identity in the last line.

By \eqref{eq:Gammaspinorpairing} and Proposition \ref{prop:3psi} we have $(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) = 0$, so $\{S_{BV}^1 + S_{BV}^2, I^{(1)}(Q)\} = 0$.

The third term gives
\begin{align*}
\{S_{BV}^3, I^{(1)}(Q)\} &= -[\Gamma(Q, \lambda), c]\wedge A^* - \frac{1}{2}\langle\rho(d_A d_A c)Q, \lambda^*\rangle \\
&= -\Gamma(Q, [\lambda, c])\wedge A^* - \frac{1}{2}(\rho([F_A, c]) Q, \lambda^*).
\end{align*}

The fourth term gives
\begin{align*}
\{S_{BV}^4, I^{(1)}(Q)\} &= \frac{1}{2}([\rho(F_A) Q, c], \lambda^*) + \Gamma(Q, [\lambda, c])\wedge A^*.
\end{align*}

Again, we get $\{S_{BV}^3 + S_{BV}^4, I^{(1)}(Q)\}$ = 0. The fifth term gives $\{S_{BV}^5, I^{(1)}(Q)\} = 0$.
\end{proof}

\begin{remark}
The previous Lemma expresses the fact that the super Yang--Mills action is supersymmetric which is one of the main results of \cite{BaezHuerta}.
\end{remark}

\begin{lemma}
One has
\[\{S_{BV}, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2}\{I^{(1)}, I^{(1)}\} = 0.\]
\end{lemma}
\begin{proof}
Evaluating the equation
\[\{S_{BV}, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2}\{I^{(1)}, I^{(1)}\} = 0\]
on $v_1, v_2\in \mf{iso}(V)$, the claim reduces to the fact that \eqref{eq:Poincareaction} defines a strict Lie action. Evaluating it on $v\in\mf{iso}(V)$ and $Q\in\Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e}-invariant. So, the only nontrivial check is for $Q_1,Q_2\in\Sigma$.

The individual terms are
\begin{align*}
\{I^{(1)}, I^{(1)}\}(Q_1, Q_2) = &-2\{I^{(1)}(Q_1), I^{(1)}(Q_2)\} \\
= &-(\rho(d_A \Gamma(Q_1, \lambda)) Q_2, \lambda^*) - \Gamma(Q_2, \rho(F_A)Q_1)\wedge A^* \\
&-(\rho(d_A \Gamma(Q_2, \lambda)) Q_1, \lambda^*) - \Gamma(Q_1, \rho(F_A)Q_2)\wedge A^*,
\end{align*}
\begin{align*}
(\d_{CE} I^{(1)})(Q_1, Q_2) &= I^{(1)}(\Gamma(Q_1, Q_2)) \\
&= -L_{\Gamma(Q_1, Q_2)}(A)\wedge A^* -(\Gamma(Q_1, Q_2).\lambda, \lambda^*) - (\Gamma(Q_1, Q_2).c) c^*
\end{align*}
and
\begin{align*}
\{S_{BV}, I^{(2)}(Q_1, Q_2)\} = &-\frac{1}{2}(Q_2, \lambda^*)(Q_1, \sd{D}_A \lambda + [c, \lambda^*]) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \sd{D}_A \lambda + [c, \lambda^*]) \\
&+\frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \sd{D}_A \lambda + [c, \lambda^*])) + \iota_{\Gamma(Q_1, Q_2)}(d_A c) c^* + d_A\iota_{\Gamma(Q_1, Q_2)} A\wedge A^* \\
&+ ([\lambda, \iota_{\Gamma(Q_1, Q_2)}A], \lambda^*) - [\iota_{\Gamma(Q_1, Q_2)} A, c] c^*
\end{align*}
The total coefficient in front of $A^*$ is
\[-\frac{1}{2}\Gamma(Q_1, \rho(F_A)Q_2) - \frac{1}{2}\Gamma(Q_2, \rho(F_A) Q_1) - L_{\Gamma(Q_1, Q_2)} A + d_A \iota_{\Gamma(Q_1, Q_2)} A.\]
Using Proposition \ref{prop:cliffordactionproperties} (property (1)) we get that the sum of the first two terms is $\iota_{\Gamma(Q_1, Q_2)}F_A$ which cancels the last two terms.

The total coefficient in front of $c^*$ is
\[-\Gamma(Q_1, Q_2).c + \iota_{\Gamma(Q_1, Q_2)}(d_A c) - [\iota_{\Gamma(Q_1, Q_2)} A, c] = 0.\]

The total coefficient in front of $\lambda^*$ is
\begin{align*}
&-\frac{1}{2}\rho(d_A \Gamma(Q_1, \lambda))Q_2 -\frac{1}{2}\rho(d_A \Gamma(Q_2, \lambda))Q_1 - \Gamma(Q_1, Q_2).\lambda \\
&+ \frac{1}{2}\rho(\Gamma(Q_1, Q_2))\sd{D}_A\lambda - \frac{1}{2}(Q_2, \sd{D}_A\lambda) Q_1 -\frac{1}{2}(Q_1, \sd{D}_A\lambda) Q_2 + [\lambda, (\Gamma(Q_1, Q_2), A)]
\end{align*}
Using Proposition \ref{prop:cliffordactionproperties} (property (2)) the first, second, fifth and sixth terms combine to
\[-\frac{1}{2} \sd{D}_A\rho(\Gamma(Q_1, \lambda))Q_2 - \frac{1}{2} \sd{D}_A\rho(\Gamma(Q_2, \lambda)) Q_1\]
which is equal to $\frac{1}{2} \sd{D}_A \rho(\Gamma(Q_1, Q_2))\lambda$ by Proposition \ref{prop:3psi}. Using the Clifford relation this term cancels the rest of the terms.
\end{proof}

Evaluating the equation
\[\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} = 0\]
on $v_1, v_2, v_3\in\mf{iso}(V)$ or on $v_1, v_2\in\mf{iso}(V)$ and $Q\in\Sigma$ we automatically get zero. Evaluating it on $v\in\mf{iso}(V)$ and $Q_1, Q_2\in\Sigma$ we get Poincar\'{e}-invariance of $I^{(2)}$.

\begin{lemma}
\[\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
for every $Q_1, Q_2, Q_3\in\Sigma$.
\end{lemma}
\begin{proof}
We have
\begin{align*}
\{I^{(1)}(Q_1), I^{(2)}(Q_2, Q_3)\} = &-\iota_{\Gamma(Q_2, Q_3)}\Gamma(Q_1, \lambda) c^* + \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) \\
&- \frac{1}{2}(Q_2, \rho(A^*)Q_1)(Q_3, \lambda^*) - \frac{1}{2}(Q_3, \rho(A^*) Q_1)(Q_2, \lambda^*).
\end{align*}

$\{I^{(1)}, I^{(2)}\}$ is obtained by cyclically symmetrizing the above expression. By Proposition \ref{prop:3psi} the cyclic symmetrization of the term with $c^*$ is zero. The Clifford relation implies that
\begin{align*}
\frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) &= -\frac{1}{2}(\Gamma(Q_2, Q_3), \Gamma(\rho(A^*)\lambda^*, Q_1)) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*) \\
&= -\frac{1}{2}(\rho(\Gamma(Q_2, Q_3)) Q_1, \rho(A^*)\lambda^*) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*).
\end{align*}
Therefore, again using Proposition \ref{prop:3psi} we see that the cyclic symmetrization of the terms with $A^*$ vanishes.
\end{proof}
